A full approximation storage multilevel method \\ for nonlinear variational inequalities

### 2023-06-17 paper/fascd.tex
start in on results section

FIXME F-cycles

@@

FIXME show results for Firedrake implementation of FASCD for the 2D classical obstacle problem (ball and spiral; Example \ref{ex:plaplacian}), 1D $p$-Laplacian obstacle problem (also Example \ref{ex:plaplacian}), advection-diffusion obstacle problem (Example \ref{ex:advectiondiffusion}), and SIA obstacle problem (Example \ref{ex:sia})

@@

>>>>

FIXME F-cycles in Algorithm \ref{alg:fascd-fcycle}

\begin{pseudofloat}[ht]
\begin{pseudo}
\pr{fascd-fcycle} \\
FIXME
\end{pseudo}
\caption{FIXME}
\label{alg:fascd-fcycle}
\end{pseudofloat}

@@

The FASCD V-cycle and F-cycle (Algorithms \ref{alg:fascd}, \ref{alg:fascd-fcycle}) have been implemented in Python using the Firedrake library \cite{Rathgeberetal2016}.  In this Section we show numerical results corresponding to several VI examples from Section \ref{sec:vi}, with a focus on the scaling of FASCD iterations as the mesh resolution increases.

\begin{example}
Consider the 2D classical, unilateral obstacle problem, namely Example \ref{ex:plaplacian} with $p=2$ and admissible set $\mathcal{K} = \{v \ge \psi\} \subset W^{1,2}(\Omega)$.  Suppose $\Omega$ is a square.  We consider two problems with very different coincidence (active) sets, the ``ball'' problem with $\psi$ equal to an upper hemisphere \cite[Chapter 12]{Bueler2021}, and the ``spiral'' problem in which $\psi$ is constructed to produce a nontrivial coincidence set \cite[Example 7.1.1]{GraeserKornhuber2009}.  FIXME show table of results
\end{example}

%REGENERATE using pefarrell-fascd/examples/
%$ timer python3 drape.py -prob ball|spiral -levs 9 -o ball|spiral.pvd -fascd_rtol 1.0e-6 -fascd_atol 1.0e-6 -fascd_cycle_type full
%$ paraview ball|spiral.pvd
%use preset "xray" and invert colors
\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.35\textwidth]{fixfigs/ball-set.png} \qquad \includegraphics[width=0.35\textwidth]{fixfigs/spiral-set.png}
\end{center}
\caption{Coincidence sets $u=\psi$ for the ball and spiral problems.}
\label{fig:ballspiral}
\end{figure}

FIXME results for 1D $p$-Laplacian obstacle problem, Example \ref{ex:plaplacian} with $p=1.5,4$; this is a good problem to visualize the problems solved on each coarser level Figure \ref{fig:imagesvcycle}

@@

FIXME results for advection-diffusion obstacle problem, Example \ref{ex:advectiondiffusion}

FIXME results for SIA obstacle problem, Example \ref{ex:sia}
